# pfm
```{r, echo = FALSE}
options(device = function(file, width = 7, height = 7, ...) {
          cairo_pdf(tempfile(), width = width, height = height, ...)
})
```
The R package **pfm** provides some utilities for dealing with FOCUS pesticide fate modelling tools,
(currently only TOXSWA cwa files), made available under the GNU public license.
This means:

    This program is free software: you can redistribute it and/or modify it under
    the terms of the GNU General Public License as published by the Free Software
    Foundation, either version 3 of the License, or (at your option) any later
    version.

    This program is distributed in the hope that it will be useful, but WITHOUT
    ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
    FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
    details.

    You should have received a copy of the GNU General Public License along with
    this program. If not, see <http://www.gnu.org/licenses/>

## Installation

You can install the package from [github](http://github.com/jranke/pfm), e.g.
using the `devtools` package.  Using `quick = TRUE` skips docs,
multiple-architecture builds, demos, and vignettes, to make installation as
fast and painless as possible.

```{r, eval = FALSE}
library(devtools)
install_github("jranke/pfm", subdir = "pkg", quick = TRUE)
```

To read in and analyse a cwa file:

```{r}
library(pfm)
example_cwa <- read.TOXSWA_cwa("00003s_pa.cwa")
plot(example_cwa)
example_cwa$get_events(c(20, 100))
example_cwa$moving_windows(c(7, 21))
print(example_cwa)
```
